%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Dave Sayles}

\moveleft.5\hoffset\centerline{sayles.dave@gmail.com\hspace{64pt}www.github.com/dgs3}

 
\moveleft1.5\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'


%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\section{Summary}

Engineering leader with 10+ years building and scaling software teams, and recent hands-on experience designing and shipping generative AI and agentic solutions. Track record of setting technical direction across multiple teams, growing engineering talent into leads and managers, and delivering within complex, matrixed organizations. Strong believer in consistent, candid feedback as the primary lever for leveling up engineers---regular 1:1s, structured growth conversations, and clear expectations mean engineers are never surprised and always improving. Fluent in Python; experienced applying LLMs, agentic AI, and GenAI tooling to real business problems.

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

{\sl Languages:} Python, JavaScript \\
{\sl AI / ML:} Large Language Models (LLMs), Generative AI, Agentic AI, Retrieval-Augmented Generation (RAG) \\
{\sl Leadership:} People Management, Technical Roadmapping, ML Infrastructure Strategy, Cross-functional Collaboration \\
{\sl Practices:} CI/CD, Observability (Prometheus), Agile/Scrum, Code Review, Systems Design

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

{\sl Bachelor of Science,} Computer Science and Digital Art \\
Union College, Schenectady, NY, 12308

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}
J. Rieffel and D. Sayles. EvoFab: A Fully Embodied Evolutionary Fabricator.  \\In: 9th International Converence on Evolvable Systems, Sep 6 2010 \\

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{Experience}

{\sl Director - Internal Tools} \hfill 2025 -- Present \\
MongoDB, New York, NY
\begin{itemize}
\item[-] Lead a 14-engineer org spanning multiple teams; set technical roadmaps and long-term infrastructure strategy aligned to department-wide priorities.
\item[-] Owned team roadmaps, OKRs, sprint execution, and systems design review across multiple concurrent workstreams. Stayed close enough to delivery details to anticipate slowdowns early---either jumping in personally to unblock critical work or rearranging priorities before bottlenecks could stall a team. Actively monitored critical rollouts in flight; when a rollout showed signs of going sideways, worked directly with the team to revise the plan, adjust scope, or restructure the approach before it became a problem.
\item[-] Practiced anticipatory management by regularly monitoring team capacity and delivery signals to get ahead of staffing gaps and technical blockers before they became problems. Accomplished this by proactively moving engineers across teams and re-scoping work to keep delivery on track.
\item[-] Anticipated a future leadership gap before it became a crisis: proactively identified senior engineers with management potential and began coaching them early---promoting them into Lead Engineers, tech leads, and staff engineers so the org would have capable leaders ready as it grew, rather than scrambling to fill gaps under pressure.
\item[-] Recognized that the org's reliance on a single Lead Engineer as the designated authority would create a structural bottleneck as teams scaled. Proactively designed and rolled out a Tech Lead role that distributed that authority, gave senior ICs a clear growth path to senior/staff positions, and gave the org the flexibility to scale without being gated on one person. The model was adopted across the wider department.
\item[-] Drove GenAI adoption across a 14-person org through a two-pronged approach: directly encouraged engineers to use Claude and Cursor in their daily workflows, and identified internal champions who amplified adoption through peer communication, lunch and learns, and team demos. Reinforced the cultural push by building tooling that demonstrated AI's potential in concrete terms---including an agentic Claude Code workflow that automatically opened pull requests from JIRA ticket descriptions, turning an abstract concept into something engineers could see and use immediately.
\item[-] Partnered with Product, Tech Leads, and Support across a matrixed organization to reduce engineering escalations from multiple per day to roughly 1--3 per week through improved tooling, documentation, and automated workflows.
\item[-] Directly led a cross-functional pod that delivered an agentic Atlas cluster-sizing tool for sales, applying LLMs to convert unstructured sales feedback into concrete, automatable infrastructure recommendations.
\end{itemize}

{\sl Senior Lead - Internal Tools} \hfill 2022 -- 2025 \\
MongoDB, New York, NY
\begin{itemize}
\item[-] Managed a 10-person org: 5 direct reports plus a team lead overseeing a sub-team of 4. Partnered closely with Product on roadmap, instrumentation strategy, and overal team execution.
\item[-] Rescued a top-10 company-initiative web app from chronic failures and zero observability to a responsive, instrumented, and trusted system that shipped reliably enough to justify continued GTM investment.
\item[-] Replaced a painful weekly, manual QA release process with automated integration tests, enabling safe and modern on-demand deployments.
\item[-] Doubled team size and split engineers into focused pods across a matrixed org, enabling parallel feature delivery without fragmenting ownership or lowering quality.
\item[-] Instituted a cadence of 6-week growth conversations and continuous feedback loops, leading to smooth yearly reviews where engineers were never surprised by growth areas or ratings.
\item[-] Reworked agile ceremonies to maximize signal: standups shrank from 30 minutes to 5, sprint planning dropped from roughly an hour to about 15 minutes.
\end{itemize}

{\sl Staff Engineer - Internal Tools} \hfill 2022 -- 2022 \\
MongoDB, New York, NY
\begin{itemize}
\item[-] Brought agile and observability (Prometheus, alerting, dashboards, error collation) to teams that had neither; deployments moved from chronic failure to stable, debuggable, and alert-driven.
\item[-] Served as technical owner and de facto product manager: authored technical roadmaps, set priorities, drove cross-team alignment, and ran sprint planning with explicit quarterly product and engineering goals.
\end{itemize}

{\sl Senior Engineer - Internal Tools} \hfill 2020 -- 2022 \\
MongoDB, New York, NY
\begin{itemize}
\item[-] Raised the bar on Operational Excellence by implementing and socializing Modern CI/CD and Git workflows, Idiomatic Python, and Integration Testing.
\item[-] Championed admin tooling that removed most direct human interaction with production databases, allowing more engineers to resolve customer issues without dangerous write access.
\item[-] Architected and implemented several web applications for GoToMarket segments and Access Management that are still in use today by the company. 
\end{itemize}

{\sl Senior Engineer} \hfill 2019 -- 2020 \\
Neverware, Inc, New York, NY
\begin{itemize}
\item[-] Neverware was acquired by Google in 2020.
\item[-] Worked on CloudReady OS, a custom fork of Chrome OS; modified system services to improve compatibility across hardware types.
\end{itemize}

{\sl Director of Engineering} \hfill July 2014 - Present \\
Neverware, Inc, New York, NY
\begin{itemize}
\item[-] Reported directly to the CEO during a major company pivot; staffed and organized the engineering team for CloudReady (a Chrome OS fork), ran the build-out, and shepherded the product through launch and continuous development cycles. CloudReady still exists today as the Google Product FlexOS.
\item[-] Built and grew engineering team from 3 to 7 engineers, plus 2 QA engineers and a technical project manager.
\item[-] Spent about ~30\% of time working on engineering tasks.
\end{itemize}

{\sl Software Engineer} \hfill Feb 2014 - July 2014 \\
Neverware, Inc, New York, NY
\begin{itemize}
\item[-] Raised the bar on Operational Excellence by implementing and socializing Modern CI/CD and Git workflows, Idiomatic Python, code review, and automated testing.
\item[-] Stabilized opaquely failing product through debugging, admin tooling, and telemetry.
\item[-] Engineer on PCReady, a localized virtualization solution for education customers that delivered ephemeral VMs.
\end{itemize}

{\sl Software Engineer} \hfill Apr 2012 - Feb 2014 \\
Makerbot Industries, Brooklyn, NY
\begin{itemize}
\item[-] MakerBot was acquired by Stratasys in 2013.
\item[-] Core developer on the \textit{MakerWare} stack: architected \textit{kaiten} (embedded Python server for Desktop 3D printers), backend \textit{conveyor} (job dispatch to slicer and driver), and \textit{s3g} printer driver.
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
