%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\newcommand{\headerSeparater}{{\hspace{16pt}--\hspace{16pt}}}
\newcommand{\sheraton}{{Sheraton New York Times Square Hotel}}

\moveleft.1\hoffset\centerline{\large\bf Cat Sayles}

\moveleft.1\hoffset\centerline{415 Argyle Rd Apt. 2T Brooklyn, NY 11218\headerSeparater 201.410.8016\headerSeparater sayles.catherine@gmail.com}

 
\moveleft.7\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}
\section{Education} \vspace{15pt}
{\sl Bachelor of Arts,} Visual Arts \& Philosophy \\
Union College, Schenectady, NY, 12308 \\
\vspace{-10pt}
\begin{itemize}
\item[-] Received 2009 Senior Meritorious Service Award: For commitment and service to the campus community.
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience} \vspace{15pt}
{\sl Project Manager and Technical Consultant} \hfill February 2018 - September 2018\\
Medaffect / Potentis Capital, New York, NY \vspace{5pt}
\newline
Managed various projects working with the companies under the Potentis Capital portfolio. Some of the projects are:
\vspace{5pt}
\begin{itemize}
\item[-] Implemented a CRM tool for the catering company "Farm Cut", managed customization with their sister company, Agile Elements. Provided QA testing. 
\item[-] Secured contract for and implemented a new HR system for all the companies and trained staff on how to use their new system.
\item[-] Implemented a time clock system for one of the sister companies and taught staff how to use their new system.
\item[-] Created SOPs for the Medaffect HR department.
\item[-] Recruited for a sales person for Farm Cut Catering.
\end{itemize}

{\sl General Manager} \hfill March 2016 - January 2018\\
Tone House / Potentis Capital, New York, NY
\begin{itemize}
\item[-] Oversaw daily operations of two locations and a staff of 40 employees.
\item[-] Handled all HR responsibilities: recruitment, hiring, firing, payroll, Health Insurance, onboarding new staff and PTO requests.
\item[-] Created schedules for Managers on Duty, Instructors, Front Desk Staff and Maintenance Departments.
\item[-] Increased efficiency by implementing software systems for scheduling, payroll, task tracking, performance reviews and communication
\item[-] Created SOPS for every department in the form of standard operating procedures (SOPs), daily management recaps, and performance reviews. 
\item[-] Provided quality assurance testing for new custom booking software for the gym. Worked with engineers from sister company Agile Elements regularly for 1 year during planning of system and implementation. Trained staff on the new software.
\end{itemize}

{\sl Client Relations Representative} \hfill July 2015 - March 2016\\
Tone House / Potentis Capital, New York, NY
\begin{itemize}
\item[-] Greeted clients at check in and ensured top quality customer service experience. 
\item[-] Maintained membership database.
\item[-] Assisted COO in daily operations and was promoted to General Manager when new studio opened.
\end{itemize}
 
{\sl Owner and Lead Event Planner} \hfill July 2013 - March 2016\\
All Natural Weddings \& Events, Brooklyn, NY
\begin{itemize}
\item[-] Founded Brooklyn based eco friendly event planning company.
\item[-] Executed and planned events with an eco-friendly and homegrown approach
\end{itemize}

{\sl Executive Board Member} \hfill December 2011 - Present\\
The Matthew Sayles Foundation For Salivary Gland Cancer, Ridgewood, NJ
\begin{itemize}
\item[-] Acts as Executive Board Member for non-profit organization
\item[-] Plans annual Music Festival and serves as Vendor Coordinator.
\end{itemize}

{\sl VIP Supervisor} \hfill February 2013 - July 2013\\
\sheraton, New York NY
\begin{itemize}
\item[-] Liaison for all VIP guests including reservations, arrivals and departures, room upgrades, and accommodated all VIP needs.
\item[-] Conceptualized, planned and executed all details for monthly VIP soirees. Duties included creating food and beverage menu with culinary team, managing budget and choosing location.
\item[-] Managed VIP club lounge and staff of 6 employees.
\end{itemize}

{\sl Executive Meeting Specialist} \hfill November 2011 - February 2013\\
\sheraton, New York NY
\begin{itemize}
\item[-] Liaison between clients and the operational departments of the hotel to ensure events are flawless by anticipating all client's needs.
\end{itemize}

{\sl Event Planner \& Concierge} \hfill October 2010 - May 2011 \\
My City Hotel \& Restaurant, Okayama Japan
\begin{itemize}
\item[-] Worked as English speaking concierge staff for hotel and planned private parties in hotel restaurant.
\end{itemize}

{\sl Recruiting Assistant \& Computer Science Instructor} \hfill July 2009 - June 2010 \\
Mildred Elley College, Albany, NY
\begin{itemize}
\item[-] Responsibilities included recruitment for the college and teaching three introductory computer science classes.
\end{itemize}

\section{Internships} \vspace{15pt}

{\sl Administration Intern \& Docent} \hfill Summer of 2008 \\
Salem Art Works Sculpture Park, Salem NY

{\sl Office of Senator Hillary Rodham Clinton} \hfill Summer of 2006 \\
Administrative Intern, Albany 2006

\end{resume}
\end{document}
